Title field: summary

### 2021-02-03 inst/examples/title.Rmd
change

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
p <- top_plot(df, "title", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

library(ggplot2)
p <- ggplot(d, aes(x = n)) +
       geom_histogram() +
       scale_x_log10() +
       scale_y_log10() +
       labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

>>>>

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "title", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
       geom_histogram(color="black", fill="white") +
       scale_x_log10() +
       scale_y_log10() +
       labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```
